Summary Tables

### 2021-11-29 summary_tables.Rmd
Regen

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- TRUE
#cities <- c('accra','sao_paulo','buenos_aires')

@@

dat[[city]] <- io[[city]]$trip_scen_sets %>% mutate(scenario = case_when(
  scenario == "Scenario 1" ~ "PED_SC", 
  scenario == "Scenario 2" ~ "CYC_SC",
  scenario == "Scenario 3" ~ "CAR_SC",
  scenario == "Scenario 4" ~ "MOT_SC",
  scenario == "Scenario 5" ~ "BUS_SC",
  scenario == "Baseline" ~ "Baseline")) %>% group_by(scenario, trip_mode, trip_distance_cat) %>% summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% mutate(city = city)

@@

for (i in 1:nrow(td)){
    val <- td %>% filter(scenario == "Baseline", trip_mode == td$trip_mode[i] & 
                           trip_distance_cat == td$trip_distance_cat[i] &
                           city == td$city[i])

    if (nrow(val) > 0){
      td$diff[i] <- val$n - td$n[i]
      td$trip_prop[i] <- round(td$n[i] / val$n, 2)
      td$dist_prop[i] <- round(td$dist[i] / val$dist, 2)

@@

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('BASELINE', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]

@@

  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

@@

for(city in cities){

  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:7] <- c("BASELINE", rownames(scen_prop))

@@

  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dist %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:7] <- c("BASELINE", rownames(scen_prop))
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

@@

for(city in cities){

  count_people <- round(sum(io[[city]]$demographic$population))
  td <- io[[city]]$true_dist %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, list(~round((.) * 365, 3)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:7] <- c("BASELINE", rownames(scen_prop))

@@

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dur %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:7] <- c("BASELINE", rownames(scen_prop))
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

@@

  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dur %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:7] <- c("BASELINE", rownames(scen_prop))
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

@@

#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2],function(x){
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = 5)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z]))
  })
  colnames(temp) <- scen_names
  temp
})
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

@@

yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]] / t(repmat(pop_by_age[[x]],5,1))*100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]), 
                                             length = 5)*100000
        )
  )

@@

### Change in YLLs per 100,000 {#change_YLL_gender_age_100k}
```{r scen_prop = "asis"}
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2], function(x) {
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    rowSums(xx[,seq(2 + y, ncol(xx), by = 5)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,c('sex','age_cat')], 1,
                          function(z)paste0(z[2], '_', z[1]))
  colnames(temp) <- scen_names
  temp
})

yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')], 1,
                                    function(z) paste0(z[2],'_',z[1])), 
                              rownames(yll_totals[[x]])),] /
          t(repmat(io[[x]]$demographic$population,5,1)) * 100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                             length = 5) * 100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

### Change in YLLs due to injury {#change_yll_injury}
```{r}
injury_totals <- lapply(io[-2], function(x) {
  xx <- x$outcomes$hb$ylls
  injury_col <- grep("inj", names(xx))[1] # Dan: This line is mine (not sure is ok)
  xxx <- sapply(1:5, function(y)
    sapply(sort(unique(xx$age_cat)), function(z)
      sum(xx[xx$age_cat == z, injury_col - 1 + y])))
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(injury_totals, "Change in YLLs due to injury in ")
```

### Change in YLLs due to PA {#change_yll_PA}
```{r}
pa_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5, function(y){
    xxx <- rowSums(xx[, pa_cols[seq(y, length(pa_cols), by = 5)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})

@@

### Change in YLLs due to AP {#change_yll_AP}
```{r}
ap_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y) {
    xxx <- rowSums(xx[, ap_cols[seq(y, length(ap_cols), by = 5)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

@@

### Change in YLLs due to injury per 100,000 {#change_yll_injury_100k}
```{r scen_prop = "asis"}
injury_rates <- lapply(cities, function(x)
  rbind(
    injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1)) * 100000,
    Total = colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                            length = 5) * 100000)
  )

@@

### Change in YLLs due to PA per 100,000 {#change_yll_PA_100k}
```{r}
pa_rates <- lapply(cities, function(x)
  rbind(
    pa_totals[[x]] / t(repmat(pop_by_age[[x]], 5, 1)) * 100000,
    Total = colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                        length = 5) * 100000))

@@

### Change in YLLs due to injury AP 100,000 {#change_yll_AP_100k}
```{r}
ap_rates <- lapply(cities, function(x)
  rbind(
    ap_totals[[x]] / t(repmat(pop_by_age[[x]], 5 ,1)) * 100000,
    Total = colSums(ap_totals[[x]]) / rep(sum(pop_by_age[[x]]),
                                          length = 5) * 100000))
names(ap_rates) <- cities
round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

@@

### Change in deaths due to disease {#change_death_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y){
    colSums(xx[, seq(y + 2, ncol(xx), by = 5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_deaths_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_', '', y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")
```

@@

### Change in deaths due to disease per 100,000 {#change_death_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]), 
                                               length = 5)*100000))

@@

### Change in YLL due to disease {#change_yll_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = 5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_ylls_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_','',y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")
```

### Change in YLL due to disease per 100,000 {#change_yll_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]),
                                               length = 5) * 100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in YLL due to disease per 100,000 in ")
```

>>>>

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- TRUE
NSCEN <- 3
#cities <- c('accra','sao_paulo','buenos_aires')

@@

for (city in cities) {

dat[[city]] <- io[[city]]$trip_scen_sets %>% 
  mutate(scenario = case_when(
    # scenario == "Scenario 1" ~ "PED_SC", 
    # scenario == "Scenario 2" ~ "CYC_SC",
    # scenario == "Scenario 3" ~ "CAR_SC",
    # scenario == "Scenario 4" ~ "MOT_SC",
    # scenario == "Scenario 5" ~ "BUS_SC",
    scenario == "Scenario 1" ~ "CYC_SC", 
    scenario == "Scenario 2" ~ "CAR_SC",
    scenario == "Scenario 3" ~ "BUS_SC",
    scenario == "Baseline" ~ "Baseline")) %>% 
  group_by(scenario, trip_mode, trip_distance_cat) %>% 
  summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% 
  mutate(city = city)

@@

for (i in 1:nrow(td)) {
    val <- td %>% filter(scenario == "Baseline", trip_mode == td$trip_mode[i] & 
                           trip_distance_cat == td$trip_distance_cat[i] &
                           city == td$city[i])

    if (nrow(val) > 0) {
      td$diff[i] <- val$n - td$n[i]
      td$trip_prop[i] <- round(td$n[i] / val$n, 2)
      td$dist_prop[i] <- round(td$dist[i] / val$dist, 2)

@@

for (city in cities) { # Loop for each city
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% 
    summarise(uid = n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% 
    group_by(trip_mode, scenario) %>% 
    summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% 
    spread(key = trip_mode, value = p) %>% 
    mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('BASELINE', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]

@@

  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
} # End loop city

@@

for (city in cities) {

  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% dplyr::filter(stage_mode != 'bus_driver') %>%
    mutate_if(is.numeric, round, digits = round_to) %>% 
    mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))

@@

  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dist %>% dplyr::filter(stage_mode != 'bus_driver') %>%
    mutate_if(is.numeric, round, digits = round_to) %>% 
    mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

@@

for (city in cities) {

  count_people <- round(sum(io[[city]]$demographic$population))
  td <- io[[city]]$true_dist %>% dplyr::filter(stage_mode != 'bus_driver') %>%
    mutate_if(is.numeric, list(~round((.) * 365, 3)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))

@@

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dur %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

@@

  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dur %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

@@

#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2],function(x){
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z]))
  })
  colnames(temp) <- scen_names
  temp
})
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

@@

yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]] / t(repmat(pop_by_age[[x]],NSCEN,1))*100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]), 
                                             length = NSCEN)*100000
        )
  )

@@

### Change in YLLs per 100,000 {#change_YLL_gender_age_100k}
```{r scen_prop = "asis"}
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2], function(x) {
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls
    rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,c('sex','age_cat')], 1,
                          function(z)paste0(z[2], '_', z[1]))
  colnames(temp) <- scen_names
  temp
})

yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')], 1,
                                    function(z) paste0(z[2],'_',z[1])), 
                              rownames(yll_totals[[x]])),] /
          t(repmat(io[[x]]$demographic$population,NSCEN,1)) * 100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                             length = NSCEN) * 100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

### Change in YLLs due to injury {#change_yll_injury}
```{r}
injury_totals <- lapply(io[-2], function(x) {
  xx <- x$outcomes$hb$ylls
  injury_col <- grep("inj", names(xx))[1] # Dan: This line is mine (not sure is ok)
  xxx <- sapply(1:NSCEN, function(y)
    sapply(sort(unique(xx$age_cat)), function(z)
      sum(xx[xx$age_cat == z, injury_col - 1 + y])))
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(injury_totals, "Change in YLLs due to injury in ")
```

### Change in YLLs due to PA {#change_yll_PA}
```{r}
pa_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:NSCEN, function(y){
    xxx <- rowSums(xx[, pa_cols[seq(y, length(pa_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})

@@

### Change in YLLs due to AP {#change_yll_AP}
```{r}
ap_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:NSCEN,function(y) {
    xxx <- rowSums(xx[, ap_cols[seq(y, length(ap_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

@@

### Change in YLLs due to injury per 100,000 {#change_yll_injury_100k}
```{r scen_prop = "asis"}
injury_rates <- lapply(cities, function(x)
  rbind(
    injury_totals[[x]]/t(repmat(pop_by_age[[x]],NSCEN,1)) * 100000,
    Total = colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                            length = NSCEN) * 100000)
  )

@@

### Change in YLLs due to PA per 100,000 {#change_yll_PA_100k}
```{r}
pa_rates <- lapply(cities, function(x)
  rbind(
    pa_totals[[x]] / t(repmat(pop_by_age[[x]], NSCEN, 1)) * 100000,
    Total = colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                        length = NSCEN) * 100000))

@@

### Change in YLLs due to injury AP 100,000 {#change_yll_AP_100k}
```{r}
ap_rates <- lapply(cities, function(x)
  rbind(
    ap_totals[[x]] / t(repmat(pop_by_age[[x]], NSCEN ,1)) * 100000,
    Total = colSums(ap_totals[[x]]) / rep(sum(pop_by_age[[x]]),
                                          length = NSCEN) * 100000))
names(ap_rates) <- cities
round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

@@

### Change in deaths due to disease {#change_death_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:NSCEN,function(y){
    colSums(xx[, seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_deaths_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_', '', y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")
```

@@

### Change in deaths due to disease per 100,000 {#change_death_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]), 
                                               length = NSCEN)*100000))

@@

### Change in YLL due to disease {#change_yll_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:NSCEN,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_ylls_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_','',y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")
```

### Change in YLL due to disease per 100,000 {#change_yll_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]),
                                               length = NSCEN) * 100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in YLL due to disease per 100,000 in ")
```
